Risk Perceptions for Wearable Devices

### 2015-03-03 benefit.tex
directory change in risk/benefit
title

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Gender Detectionben & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{genderdetectionben} \\ 
Age Detectionben & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{agedetectionben} \\ 
Discreet Microphoneben & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetmicrophoneben} \\ 
Cubetasticben & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{cubetasticben} \\ 
Fitness Trackersben & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{fitnesstrackersben} \\ 
Voice Based Emotion Detectionben & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicebasedemotiondetectionben} \\ 
Facial Detectionben & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{facialdetectionben} \\ 
Discreet Video Cameraben & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetvideocameraben} \\ 
Google Glassben & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{googleglassben} \\ 
Smartwatchesben & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartwatchesben} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{HandgunBenefit} \\ 
Facial Recognitionben & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{facialrecognitionben} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{LawnmowerBenefit} \\ 
Speech To Textben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{speechtotextben} \\ 
Voice Recognitionben & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicerecognitionben} \\ 
Language Detectionben & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{languagedetectionben} \\ 
Heart Rate Detectionben & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{heartratedetectionben} \\ 
Location Trackingben & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{locationtrackingben} \\ 
Emailben & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{emailben} \\ 
Smartphonesben & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartphonesben} \\ 
Laptopsben & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{laptopsben} \\ 
Internetben & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{internetben} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{ElectricityBenefit} \\ 
Ben & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{ben} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 risk.tex
directory change in risk/benefit
title

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslocationtrackingrisk} \\ 
Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesspeechtotextrisk} \\ 
Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetmicrophonerisk} \\ 
Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartwatchesrisk} \\ 
Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslanguagedetectionrisk} \\ 
Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslaptopsrisk} \\ 
Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartphonesrisk} \\ 
Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgoogleglassrisk} \\ 
Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescubetasticrisk} \\ 
Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgenderdetectionrisk} \\ 
Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicerecognitionrisk} \\ 
Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicebasedemotiondetectionrisk} \\ 
Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfitnesstrackersrisk} \\ 
Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesagedetectionrisk} \\ 
Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialdetectionrisk} \\ 
Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesemailrisk} \\ 
Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesheartratedetectionrisk} \\ 
Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetvideocamerarisk} \\ 
Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesinternetrisk} \\ 
Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialrecognitionrisk} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesLawnmowerRisk} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesMotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesHandgunRisk} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| p{2cm} | p{1cm} | p{1cm} | p{1cm} | c |}
\hline
Technology & Q1 &  Median & Q3 & Distribution  \\ 
\hline
Location Tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslocationtrackingrisk} \\ 
Speech To Text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesspeechtotextrisk} \\ 
Discreet Microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetmicrophonerisk} \\ 
Smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartwatchesrisk} \\ 
Language Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslanguagedetectionrisk} \\ 
Laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslaptopsrisk} \\ 
Smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartphonesrisk} \\ 
Google Glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgoogleglassrisk} \\ 
Cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablescubetasticrisk} \\ 
Gender Detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgenderdetectionrisk} \\ 
Voice Recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicerecognitionrisk} \\ 
Voice Based Emotion Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicebasedemotiondetectionrisk} \\ 
Fitness Trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfitnesstrackersrisk} \\ 
Age Detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesagedetectionrisk} \\ 
Facial Detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialdetectionrisk} \\ 
Email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesemailrisk} \\ 
Heart Rate Detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesheartratedetectionrisk} \\ 
Discreet Video Camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetvideocamerarisk} \\ 
Internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesinternetrisk} \\ 
Facial Recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialrecognitionrisk} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesLawnmowerRisk} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesMotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesHandgunRisk} \\ 
 & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tablesrisk} \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

### 2015-03-03 riskbenefit.tex
directory change in risk/benefit
title

location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslocationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesspeechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslanguagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{../languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tableslaptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{../laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablessmartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{../smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgoogleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablescubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesgenderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesvoicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesagedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{../agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{../facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesemailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{../emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesheartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{../heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesdiscreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesinternetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesfacialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{../facialrecognitionben} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesLawnmowerRisk} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{../HandgunBenefit} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesMotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../tablesHandgunRisk} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{../ElectricityBenefit} \\ 
 & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../tablesrisk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{../ben} \\ 

>>>>

location tracking & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslocationtrackingrisk} & 40.0 & 20.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{locationtrackingben} \\ 
speech to text & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesspeechtotextrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{speechtotextben} \\ 
discreet microphone & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetmicrophonerisk} & 15.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetmicrophoneben} \\ 
smartwatches & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartwatchesrisk} & 20.0 & 10.0 & 35.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartwatchesben} \\ 
language detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslanguagedetectionrisk} & 35.0 & 15.0 & 60.0 & \includegraphics[width = 2cm, height = 0.5cm]{languagedetectionben} \\ 
laptops & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tableslaptopsrisk} & 60.0 & 40.0 & 80.0 & \includegraphics[width = 2cm, height = 0.5cm]{laptopsben} \\ 
smartphones & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablessmartphonesrisk} & 50.0 & 30.0 & 75.0 & \includegraphics[width = 2cm, height = 0.5cm]{smartphonesben} \\ 
google glass & 10.0 & 10.0 & 20.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgoogleglassrisk} & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{googleglassben} \\ 
cubetastic & 10.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablescubetasticrisk} & 15.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{cubetasticben} \\ 
gender detection & 10.0 & 10.0 & 13.5 & \includegraphics[width = 2cm, height = 0.5cm]{tablesgenderdetectionrisk} & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{genderdetectionben} \\ 
voice recognition & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicerecognitionrisk} & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicerecognitionben} \\ 
voice based emotion detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesvoicebasedemotiondetectionrisk} & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{voicebasedemotiondetectionben} \\ 
fitness trackers & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfitnesstrackersrisk} & 18.5 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{fitnesstrackersben} \\ 
age detection & 10.0 & 10.0 & 15.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesagedetectionrisk} & 12.0 & 10.0 & 22.0 & \includegraphics[width = 2cm, height = 0.5cm]{agedetectionben} \\ 
facial detection & 10.0 & 10.0 & 25.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialdetectionrisk} & 20.0 & 10.0 & 34.0 & \includegraphics[width = 2cm, height = 0.5cm]{facialdetectionben} \\ 
email & 10.0 & 10.0 & 18.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesemailrisk} & 50.0 & 29.0 & 77.5 & \includegraphics[width = 2cm, height = 0.5cm]{emailben} \\ 
heart rate detection & 10.0 & 10.0 & 10.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesheartratedetectionrisk} & 40.0 & 26.0 & 65.0 & \includegraphics[width = 2cm, height = 0.5cm]{heartratedetectionben} \\ 
discreet video camera & 12.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesdiscreetvideocamerarisk} & 20.0 & 15.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{discreetvideocameraben} \\ 
internet & 15.0 & 10.0 & 31.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesinternetrisk} & 65.0 & 45.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{internetben} \\ 
facial recognition & 17.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesfacialrecognitionrisk} & 22.0 & 12.5 & 42.5 & \includegraphics[width = 2cm, height = 0.5cm]{facialrecognitionben} \\ 
Lawnmower & 20.0 & 12.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesLawnmowerRisk} \\ 
Motorcycle & 20.0 & 12.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{MotorcycleBenefit} \\ 
Handgun & 20.0 & 10.0 & 30.0 & \includegraphics[width = 2cm, height = 0.5cm]{HandgunBenefit} \\ 
Lawnmower & 24.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{LawnmowerBenefit} \\ 
Electricity & 25.0 & 15.0 & 40.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesElectricityRisk} \\ 
Motorcycle & 45.0 & 27.0 & 70.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesMotorcycleRisk} \\ 
Handgun & 60.0 & 40.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{tablesHandgunRisk} \\ 
Electricity & 88.0 & 50.0 & 100.0 & \includegraphics[width = 2cm, height = 0.5cm]{ElectricityBenefit} \\ 
 & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{tablesrisk} & 100.0 & nan & nan & \includegraphics[width = 2cm, height = 0.5cm]{ben} \\ 
